---
title: "Statistical Consulting"
packages:
  any::knitr
  any::rmarkdown
---

I have worked as a consultant with Statistical Consulting Services (SCS) at the University of Connecticut since July, 2022. As of August, 2023, I have held the title of SCS Administrative Specialist. For more details surrounding SCS and our mission, please visit <https://statsconsulting.uconn.edu/>. In this position, I have collaborated with a variety of students and faculty from departments such as Kinesiology, Psychology, Civil and Environmental Engineering, Physiology and Neurobiology, Speech and Language, School of Pharmacy, School of Social Work, and School of Public Health. I have also had the experience of working with external clients such as Hartford HealthCare. Working under Director of SCS, Dr. Timothy E. Moore, and these collaborative experiences have elevated my capabilities as a researcher, enhanced my proficiency in R, facilitated exploration into various statistical coding languages, and enriched my skills as an educator.

# Projects

All projects are overseen by Dr. Timothy E. Moore.

## Improving Firefighter Navigation with Haptic Feedback

Primary Contact: Andrew Slater, Ph.D. Candidate (Dept. of Biomedical Engineering)

Methods: We fit a logistic regression model on the binary response variable for success/failure. We include two fixed effects covariates for path and trial_type (belt vs. no belt), and include an interaction term between the two fixed effects covariates. We also include a random effect for ID, accounting for the fact that we have repeated observations on individual firefighters. By observing the fitted models, we are able to determine which covariates have a significant impact on the response (success/failure).

Conducted two experiments:

#### Experiment 1

-   Aim: Determine if NHC communication can outperform a pass-alarm in navigating to a disabled firefighter.

-   Tasks:

    -   navigate to a specific location withing the environment either while seeking out a clearly audible PASS alarm, or while being guided by the V-T Belt system

    -   determine the bearing to the target point at start of trail

    -   determine bearing to start point at end of trial

-   Failure: timeout before reaching target location

```{r, warning=FALSE, echo=FALSE, results='hide', message=FALSE}
# necessary package to read in data
library(readxl) 
library(dplyr)

############################### Data setup #####################################

library(readxl) # necessary package to read in .xlsx file
# read in the data
dat1 <- read_xlsx("FPL Consolidated Trial Data_update.xlsx", sheet = 1, 
                  na = "NA")

dat1 <- janitor::clean_names(dat1) 

# add an additional column denoting success as a binary variable; 0 = failure and 1 = success
dat1$success.bin <- ifelse(dat1$success=="yes", 1, 0)

#------------------------------------------------------------------------------#
# Generalized Linear Mixed Effects Models - Success as Binary Response Variable #

# in this section, we fit logistic regression models with trial_type, path, ...
# ... and the interaction between trial_type and path as fixed effects; we ...
# ... also include participant_number as a random effects term. 

##### Fit the models #####
library(glmmTMB) # linear and generalized mixed-effects models (with extensions) 
library(dplyr) # package to use piping for data manipulation

# Experiment 1
glmm1 <- glmmTMB(success.bin ~ trial_type*path + (1|participant_number),
                 data = dat1 %>% filter(experiment==1), 
                 family = binomial)

# Experiment 2
glmm2 <- glmmTMB(success.bin ~ trial_type*path + (1|participant_number),
                 data = dat1 %>% filter(experiment==2), 
                 family = binomial)

```

```{r, echo=FALSE, eval=FALSE}
##### Visualization #####

library(ggplot2) # package for visualization

# Success Plotting
ggplot(data = dat1 %>% filter(experiment==1), 
       aes(x=trial_type, y = success.bin, color = trial_type), size = 3)+
  geom_jitter(width = 0.5, height=0.05)+
  facet_grid(~path)

```

```{r, warning=FALSE}
# package to examine the estimated marginal means
library(emmeans)
# estimated marginal means
em_glmm1 <- emmeans(glmm1, ~ trial_type | path)
ip_glmm1 <- emmip(em_glmm1, ~ trial_type | path, type = "response", 
                  bias.adjust = TRUE)
ip_glmm1
```

```{r, echo=FALSE}
library(performance)
# check posterior predictive power
check_posterior_predictions(glmm1, 100)
```

#### Experiment 2

-   Aim: Determine if NHC can better route an egress path for firefighters over traditional methods.

-   Tasks:

    -   firefighter led through the building and asked to retrace steps back to starting location using tradition methods, or firefighter placed at the return starting point and used the V-Tbelt

    -   determine the bearing to the target point at start of trail

    -   determine bearing to start point at end of trial

-   Failure: timeout before reaching target or off return path for more than 20 seconds

```{r, echo=FALSE, eval=FALSE}
##### Visualization #####
library(ggplot2) # package for visualization
# Success Plotting
ggplot(data = dat1 %>% filter(experiment==2), aes(x = trial_type, 
                                                  y = success.bin, 
                                                  color = trial_type), size = 3) +
  geom_jitter(width = 0.5, height=0.05) +
  facet_grid(~path)
```

```{r, warning=FALSE}
# package to examine the estimated marginal means
library(emmeans)
# estimated marginal means
em_glmm2 <- emmeans(glmm2, ~ trial_type | path)
ip_glmm2 <- emmip(em_glmm2, ~ trial_type | path, type = "response", 
                  bias.adjust = TRUE)
ip_glmm2
```

## Bidirectional Relationship Between Food Security and Smoking

Primary Contact: Jon Phillips, Ph.D. (Assist. Prof., UConn School of Social Work)

Method: Cross-lagged panel models with covariates

## Analyzing the Impact of Pacemaker Status on the Survival of Heart Transplant Patients

Primary Contact: Cesar Rodrigo Zoni, Postdoctoral Researcher (UCONN Health)

Method: Survival analysis utilizing multi-state modeling of time-to-event data

## Comparing Outcomes in High-Risk Populations Before and After Adjusting Allocation and Prioritization of Organ Transplants

Primary Contact: William L. Baker, Pharm.D. (Assoc. Prof., Dept. of Pharmacy Practice)

Method: Multiple imputation by Fine and Gray competing risk models

## Using 30-Day Modified Rankin Scale Score to Predict 90-Day Score in Patients with Intracranial Hemorrhage: Derivation and Validation of Prediction Model

Primary Contact: William L. Baker, Pharm.D. (Assoc. Prof., Dept. of Pharmacy Practice)

Methods: Ordinal beta regression, mortality risk score models
