---
title: "Teaching"
---

My dedication to teaching and mentorship has been exemplified through the effort I have given to the different leadership roles I have held as a Graduate Assistant at the University of Connecticut. As the primary instructor, the feedback I have received from student evaluations supports my level of commitment to fostering growth in others while continually advancing myself. The one-on-one tutoring positions I have held showcased my capacity to build strong connections with students and elevated my capability of providing relatable examples tailored to the individual. My experience in these roles has refined my ability to communicate statistical concepts, enhancing my adaptability to diverse learning needs. Furthermore, I have increased proficiency in writing through the recommendation letters I have been asked to write for students. Beyond traditional teaching roles, I organized workshops introducing R to faculty and students from diverse disciplines, fostering a cross-disciplinary understanding of statistical tools.

# Courses - Primary Instructor

### Introduction to Statistics (STAT1000Q)

-   Summer 2021

    ```{r, echo=FALSE, out.width="2\\linewidth"}
    knitr::include_graphics("summer2021-1000-set.pdf")
    ```

-   Summer 2022

-   Fall 2022

    ```{r, echo=FALSE, out.width="2\\linewidth"}
    knitr::include_graphics("fall2022-1000-set.pdf")
    ```

-   Fall 2023

    ```{r, echo=FALSE, out.width="2\\linewidth"}
    knitr::include_graphics("fall2023-1000-set.pdf")
    ```

-   Spring 2024

### Elementary Concepts of Statistics (STAT1100Q)

-   Fall 2023

    ```{r, echo=FALSE, out.width="2\\linewidth"}
    knitr::include_graphics("fall2023-1100-set.pdf")
    ```

### Introduction to Mathematical Statistics II (STAT3445Q)

-   Spring 2022

    ```{r, echo=FALSE, out.width="2\\linewidth"}
    knitr::include_graphics("spring2022-3445-set.pdf")
    ```
